### 2021-06-23 publications/2020-03-paper/changes/Appendix-revised.tex
Adds 'track changes' copy
fixes references

\begin{table}[H]
\centering
	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Brief\cite{carbonbrief_carbon_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{0.55\textwidth}{p{0.05\textwidth} p{0.15\textwidth} p{0.15\textwidth} p{0.15\textwidth}}
		\hline
\textbf{Year} & \textbf{Model emissions} & \textbf{Actual emissions} & \textbf{Error} \\
  & (Mt CO$_2$-eq.) & (Mt CO$_2$-eq.) &  \\
\hline
2013 & 603.62 & 592.4 & 1.89 \% \\
2014 & 582.27 & 572.6 & 1.69 \% \\
2015 & 572.53 & 560.3 & 2.18 \% \\
2016 & 565.94 & 552.8 & 2.38 \% \\
\hline 
	\end{tabularx}
\label{ic-co2}
\end{table}

@@

 & (MUSD/GW) & (MUSD/GW) & (MUSD/GWh) & (Years)  &  & (gCO$_2$/kWh)  &  \\

@@

\gls{USC} \cite{eia_cost_2020,ipcc_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
\gls{lng}\cite{eia_cost_2020,ipcc_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
Nuclear \cite{eia_cost_2020,ipcc_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\

@@

Solar \cite{eia_cost_2020,ipcc_climate_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\

@@

\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\

@@

\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\

@@

\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\

@@

 \cite{eia_cost_2020,ipcc_climate_2014} & 1422(2050) &  & &  &  &  & \\

@@

 \cite{eia_cost_2020,ipcc_climate_2014} & 4091(2050) &  &  &  &  &  & \\

>>>>

\begin{table}[H]
\centering
	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Brief\cite{noauthor_carbon_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{0.55\textwidth}{p{0.05\textwidth} p{0.15\textwidth} p{0.15\textwidth} p{0.15\textwidth}}
		\hline
\textbf{Year} & \textbf{Model emissions} & \textbf{Actual emissions} & \textbf{Error} \\
  & (Mt CO$_2$-eq.) & (Mt CO$_2$-eq.) &  \\
\hline
2013 & 603.62 & 592.4 & 1.89 \% \\
2014 & 582.27 & 572.6 & 1.69 \% \\
2015 & 572.53 & 560.3 & 2.18 \% \\
2016 & 565.94 & 552.8 & 2.38 \% \\
\hline 
	\end{tabularx}
\label{ic-co2}
\end{table}

@@

 & (MUSD/GW) & (MUSD/GW) & (MUSD/GWh) & (Years)  &  & (gCO$_2$\added{-eq} /kWh)  &  \\

@@

\gls{USC} \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
\gls{lng}\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
Nuclear \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\

@@

Solar \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\

@@

\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\

@@

\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\

@@

\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\

@@

 \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1422(2050) &  & &  &  &  & \\

@@

 \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 4091(2050) &  &  &  &  &  & \\

### 2021-06-23 publications/2020-03-paper/revisions/Appendix.tex
adds response to reviewer 2
fixes references

\begin{table}[H]
	\caption{Data for defining the initial condition across all simulations.}
	\vspace{0.1in}
	\begin{tabularx}{0.75\textwidth}{p{0.15\textwidth} p{0.15\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
		\hline
\textbf{Technology} & \textbf{\gls{lcoe}} \cite{lazard_lazards_2016} & \textbf{Emission} & \textbf{Year of total}\\
  & (USD/kWh) & \textbf{coefficients} \cite{noauthor_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
\hline
Coal & 0.06 & 943 & 2030 \\
\gls{lng} & 0.08 & 599 & 2030 \\
Oil & 0.39 & 738 & 2030 \\
Nuclear & 0.11 & 21 & 2069 \\
Hydro & 0.05 & 11 & N.A. \\
Geothermal & 0.12 & 13 & N.A. \\
Wind & 0.11 & 25 & 2040 \\
Solar & 0.15 & 37 & 2040 \\
\hline 
\end{tabularx}
\label{init-eco}
\end{table}

@@

\begin{table}[H]
	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Brief\cite{carbonbrief_carbon_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{0.55\textwidth}{p{0.05\textwidth} p{0.15\textwidth} p{0.15\textwidth} p{0.15\textwidth}}
		\hline
\textbf{Year} & \textbf{Model emissions} & \textbf{Actual emissions} & \textbf{Error} \\
  & (Mt CO$_2$-eq.) & (Mt CO$_2$-eq.) &  \\
\hline
2013 & 603.62 & 592.4 & 1.89 \% \\
2014 & 582.27 & 572.6 & 1.69 \% \\
2015 & 572.53 & 560.3 & 2.18 \% \\
2016 & 565.94 & 552.8 & 2.38 \% \\
\hline 
	\end{tabularx}
\label{ic-co2}
\end{table}

@@

@@

 & (MUSD/GW) & (MUSD/GW) & (MUSD/GWh) & (Years)  &  & (gCO$_2$/kWh)  &  \\

@@

\gls{USC} \cite{eia_cost_2020,ipcc_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
\gls{lng}\cite{eia_cost_2020,ipcc_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
Nuclear \cite{eia_cost_2020,ipcc_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\

@@

\begin{table}[H]
	\caption{Nameplate capacity deployment limits.}
	\vspace{0.1in}
	\begin{tabularx}{0.7\textwidth}{p{0.35\textwidth} p{0.35\textwidth} }
		\hline
\textbf{Technology} & \textbf{Net Capacity} \textbf{Limit} (GW)\\
\hline
Photovoltaic \cite{isep_53_2018} & 332 \\
Onshore wind \cite{heger_wind_2016,kato_energy_2016} & 180 \\
Offshore wind (fixed) \cite{heger_wind_2016,kato_energy_2016}& 130 \\
Offshore wind (floating) \cite{heger_wind_2016,kato_energy_2016}& 260 \\
Nuclear & 50 (Scenarios 3 \& 4) \\
 & 100 (Scenario 2) \\
\gls{PWS} \cite{pinaud_technical_2013} & 100 (Scenario 5) \\
\hline 
\end{tabularx}
\label{caplim}
\end{table}

\begin{table}[H]
%\begin{minipage}{\textwidth} 
	\caption{Nameplate capacity growth rates.}
	\vspace{0.1in}
	\begin{tabularx}{0.8\textwidth}{p{0.35\textwidth} p{0.45\textwidth}}
		\hline
\textbf{Technology} & \textbf{Maximum Annual Growth Rate} \\
%  & \textbf{Growth Rate}   \\
\hline
Nuclear (2027 onwards) & +5 reactors \\
Solar and emerging solar \cite{irena_renewable_2020} & 40\%  \\
Onshore wind \cite{irena_renewable_2020} & 25\% \\
Offshore wind(Fixed) \cite{irena_renewable_2020} & 20\% \\
Offshore wind(Floating) \cite{irena_renewable_2020} & 20\% \\
Li-ion storage & 30\% \\
Natural gas &  50\% \\
\gls{USC} & 50\% \\
All emerging technologies & 40\% (Years 1-5) \\
& 60\% (Years 6-10) \\
 & 40\% (Years 11-15) \\
 & 30\% (Years 16-) \\
\hline 
\end{tabularx}
\label{growrate}
%\end{minipage}
\end{table}

\begin{table}[H]
	\caption{Miscellaneous model parameters and assumptions.}
	\vspace{0.1in}
	\begin{tabularx}{0.5\textwidth}{p{0.3\textwidth} p{0.2\textwidth}}
		\hline
\textbf{Parameter} & \textbf{Value} \\
\hline
Currency & MUSD 2015 \\
Activity unit & GWh\\
Discount rate & 5\% \\
Transmission efficiency & 90 \% \\
Li-ion discharge time \cite{mongird_energy_2019} & 4h \\
Li-ion E/P ratio \cite{mongird_energy_2019} & 4  \\
Li-ion depth-of-discharge \cite{mongird_energy_2019} & 80\% \\
Li-ion lifetime cycles \cite{mongird_energy_2019} & 3500  \\
\hline 
	\end{tabularx}
\label{misc-assump}
\end{table}

>>>>

\begin{table}[H]
\centering
	\caption{Data for defining the initial condition across all simulations.}
	\vspace{0.1in}
	\begin{tabularx}{0.75\textwidth}{p{0.15\textwidth} p{0.15\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
		\hline
\textbf{Technology} & \textbf{\gls{lcoe}} \cite{lazard_lazards_2016} & \textbf{Emission} & \textbf{Year of total}\\
  & (USD/kWh) & \textbf{coefficients} \cite{noauthor_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
\hline
Coal & 0.06 & 943 & 2030 \\
\gls{lng} & 0.08 & 599 & 2030 \\
Oil & 0.39 & 738 & 2030 \\
Nuclear & 0.11 & 21 & 2069 \\
Hydro & 0.05 & 11 & N.A. \\
Geothermal & 0.12 & 13 & N.A. \\
Wind & 0.11 & 25 & 2040 \\
Solar & 0.15 & 37 & 2040 \\
\hline 
\end{tabularx}
\label{init-eco}
\end{table}

@@

\begin{table}[H]
\centering
	\caption{Initial condition for CO$_2$ emissions compared with data from the Carbon Brief\cite{noauthor_carbon_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{0.55\textwidth}{p{0.05\textwidth} p{0.15\textwidth} p{0.15\textwidth} p{0.15\textwidth}}
		\hline
\textbf{Year} & \textbf{Model emissions} & \textbf{Actual emissions} & \textbf{Error} \\
  & (Mt CO$_2$-eq.) & (Mt CO$_2$-eq.) &  \\
\hline
2013 & 603.62 & 592.4 & 1.89 \% \\
2014 & 582.27 & 572.6 & 1.69 \% \\
2015 & 572.53 & 560.3 & 2.18 \% \\
2016 & 565.94 & 552.8 & 2.38 \% \\
\hline 
	\end{tabularx}
\label{ic-co2}
\end{table}

@@

\centering

@@

 & (MUSD/GW) & (MUSD/GW) & (MUSD/GWh) & (Years)  &  & (gCO$_2$-eq/kWh)  &  \\

@@

\gls{USC} \cite{eia_cost_2020, intergovernmental_panel_on_climate_change_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
\gls{lng}\cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
Nuclear \cite{eia_cost_2020,intergovernmental_panel_on_climate_change_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\

@@

\begin{table}[H]
\centering
	\caption{Nameplate capacity deployment limits.}
	\vspace{0.1in}
	\begin{tabularx}{0.7\textwidth}{p{0.35\textwidth} p{0.35\textwidth} }
		\hline
\textbf{Technology} & \textbf{Net Capacity} \textbf{Limit} (GW)\\
\hline
Photovoltaic \cite{isep_53_2018} & 332 \\
Onshore wind \cite{heger_wind_2016,kato_energy_2016} & 180 \\
Offshore wind (fixed) \cite{heger_wind_2016,kato_energy_2016}& 130 \\
Offshore wind (floating) \cite{heger_wind_2016,kato_energy_2016}& 260 \\
Nuclear & 50 (Scenarios 3 \& 4) \\
 & 100 (Scenario 2) \\
\gls{PWS} \cite{pinaud_technical_2013} & 100 (Scenario 5) \\
\hline 
\end{tabularx}
\label{caplim}
\end{table}

\begin{table}[H]
\centering
%\begin{minipage}{\textwidth} 
	\caption{Nameplate capacity growth rates.}
	\vspace{0.1in}
	\begin{tabularx}{0.8\textwidth}{p{0.35\textwidth} p{0.45\textwidth}}
		\hline
\textbf{Technology} & \textbf{Maximum Annual Growth Rate} \\
%  & \textbf{Growth Rate}   \\
\hline
Nuclear (2027 onwards) & +5 reactors \\
Solar and emerging solar \cite{irena_renewable_2020} & 40\%  \\
Onshore wind \cite{irena_renewable_2020} & 25\% \\
Offshore wind(Fixed) \cite{irena_renewable_2020} & 20\% \\
Offshore wind(Floating) \cite{irena_renewable_2020} & 20\% \\
Li-ion storage & 30\% \\
Natural gas &  50\% \\
\gls{USC} & 50\% \\
All emerging technologies & 40\% (Years 1-5) \\
& 60\% (Years 6-10) \\
 & 40\% (Years 11-15) \\
 & 30\% (Years 16-) \\
\hline 
\end{tabularx}
\label{growrate}
%\end{minipage}
\end{table}

\begin{table}[H]
\centering
	\caption{Miscellaneous model parameters and assumptions.}
	\vspace{0.1in}
	\begin{tabularx}{0.5\textwidth}{p{0.3\textwidth} p{0.2\textwidth}}
		\hline
\textbf{Parameter} & \textbf{Value} \\
\hline
Currency & MUSD 2015 \\
Activity unit & GWh\\
Discount rate & 5\% \\
Transmission efficiency & 90 \% \\
Li-ion discharge time \cite{mongird_energy_2019} & 4h \\
Li-ion E/P ratio \cite{mongird_energy_2019} & 4  \\
Li-ion depth-of-discharge \cite{mongird_energy_2019} & 80\% \\
Li-ion lifetime cycles \cite{mongird_energy_2019} & 3500  \\
\hline 
	\end{tabularx}
\label{misc-assump}
\end{table}
